Functional pant indicators - wetland, indicator documentation

### 2023-04-14 DRAFT_functional plant indicators_wetland.Rmd
fpi wetland result analyses continued

```{r}
head(results.wetland[['2-sided']])
```

>>>>

```{r}
head(results.wetland[['2-sided']])
```
#### Scaled value analyses

```{r}
### scaled values by NiN-hovedtype
res <- results.wetland[['2-sided']]

res2 <- 
  res %>% 
  pivot_longer(
    cols = c("Light1","Light2","Moist1","Moist2","pH1","pH2","Nitrogen1","Nitrogen2"),
    names_to = "fp_ind",
    values_to = "scaled_value",
    values_drop_na = TRUE
  )
head(res2)

ggplot(res2, aes(x=hovedtype_rute, y=scaled_value, fill=fp_ind)) + 
  geom_boxplot()

ggplot(res2, aes(x=hovedtype_rute, y=scaled_value, fill=fp_ind)) + 
  geom_hline(yintercept=0.6, linetype="dashed") + 
  geom_violin() +
  geom_boxplot(width=0.2, color="grey") +
  facet_wrap(~factor(fp_ind,levels=c("Light1","Moist1","pH1","Nitrogen1","Light2","Moist2","pH2","Nitrogen2")), ncol = 4)
